Stack Safety as a Security Property

### 2021-06-17 submission2/response_formal.txt

   The dynamic nature of this boundary makes it an issue with 
   functions that cannot be statically proven safe, but whose data
   still need to be protected when they are behaving safely.
   For a contrived example, consider a function that stores some
   private state, but takes an argument "unsafe" and, if called with
   "unsafe" set to 1, violates the reasonableness constraints. In
   the StkTokens model, we can never guarantee the safety of the
   data even if called with "unsafe" set to 0.

   We will expand on such an example in the revised version.

2. Skorstengaard's approach to proving safety via fully abstract overlay
   semantics relies on the abstract machine being architecturally similar to
   the concrete one (beyond the specific call and return semantics that
   distinguish them). This makes it less portable: each architecture it
   applies to needs its own abstract machine. Our properties should apply
   directly to a wide range of architectures.

3. We also differ from Skorstengaard et. al. in the nature of our
   safety definition.  We use the language of formal security
   properties to apply well-established concepts and formal techniques
   of non-interference. Thus, we define our properties in terms of
   traces of memory and register states, rather than in terms of an
   ad-hoc abstract machine that is asserted to be "stack safe by construction."
   Which approach is better may be a matter of taste, but we believe that our
   alternative has the merit of explicitly relating stack safety to existing
   notions of security.

@@

Delimited continuations are not supported by our base model, so a language
that has them would violate stack safety. We do extend the base model with
argument passing on the stack to demonstrate how it can accommodate a
language feature that shares stack data between callers and callees, but a
similar extension to delimited continuations would be more complex.

This distinction -- between features that could be added without changing
the properties and ones that would require enhanced properties -- is
important, and we will clarify in section 2 which features fall into which
category.

Some features that can be added/changed without changing the properties:
- a heap, as stated
- calling convention choices, like whether or not to have a frame pointer
- the machine's ISA

Features that cannot be supported without changes to the model:
- address-taken locals (would be similar to argument passing, but
  would benefit from more sophisticated, heap-like memory models)
- exceptions (needs annotations of throw/catch points)
- continuations (would be similar to argument passing)
- runtime code generation (needs dynamic code annotations)
- parallelism (needs fundamental changes to step, trace models)
